\documentclass[../Report.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}
    \vspace{1cm}
    \large
    I would like to express my sincere gratitude and appreciation to all those who have supported and 
    contributed to the completion of my dissertation project.
    \\~\\
    \noindent First and foremost, I am deeply grateful to my supervisor, \textbf{Professor Anant Pandey}, for his 
    unwavering guidance, invaluable insights, and continuous support throughout the entire research process. 
    His expertise, patience, and commitment to my academic growth have been instrumental in shaping the direction 
    and quality of this dissertation.
    \\~\\
    \noindent I also extend my heartfelt appreciation to our teacher-in-charge \textbf{Dr.\ Pratima Vyas} and all 
    the faculty members of Department of Physics at \textbf{Sri Venkateswara College, University of Delhi} for their 
    dedication to imparting knowledge, fostering critical thinking, and creating a stimulating academic environment.
    Their lectures, seminars, and scholarly discussions have expanded my intellectual horizons and provided a solid 
    foundation for my dissertation work.
    \\~\\
    \noindent 
    I am grateful to the staff and personnel of the Sri Vankateswara College library and research facilities for their 
    assistance in accessing relevant literature and resources. Their support has been vital in conducting 
    comprehensive and in-depth research for my project.
    \\~\\
    \noindent 
    I would like to express my deepest gratitude to my family and friends for their unwavering support, 
    encouragement, and understanding throughout this challenging journey. Their belief in my abilities and their 
    constant motivation have been a source of strength and inspiration.
    \\~\\
    \noindent 
    Lastly, I would like to acknowledge \textbf{Ms.Sayali Gadre} and \textbf{Ms.Devanshi Sharma} who willingly 
    volunteered their time and shared their valuable insights for the purpose of my research. Their contributions 
    have enriched my work and provided a real-world perspective to my study.
    \\~\\
    \noindent 
    To everyone who has contributed directly or indirectly to the completion of this dissertation project, I am 
    truly grateful for your support and encouragement. Your involvement has played a significant role in my 
    academic and personal growth.
    \\~\\
    \noindent 
    Thank you all for being an integral part of this journey.
    \vspace{1in}\\
    \begin{flushleft}
        \textbf{Meemik Roy}\\
        Department of Physics\\
        Sri Venkateswara College\\
        University of Delhi\\
        Roll No: 1820028\\
        Examination Roll No: 20079567027
    \end{flushleft}
\end{document}